---
title: "My first rmarkdown"
author: "Mark Andrews"
date: "29/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r primes}
primes <- c(2, 3, 5, 7, 11, 13)
sum(primes)
```

```{r primes_sq}
primes^2 
```

# Load up the `tidyverse`

The following code will load up the `tidyverse` package, which is a package of packages.

```{r load_packages}
library(tidyverse)
```

## Load the data

This will load a data frame from a URL.
```{r load_data}
weight_df <- read_csv("https://tinyurl.com/irss01weight")
```

This data frame has `r nrow(weight_df)` observations and `r ncol(weight_df)` variables.

## A scatterplot

The following *scatterplot* will **show** each person's weight as function of their height, and show the lines of best fit. 

```{r scatterplot, echo=FALSE}
ggplot(weight_df,
       mapping = aes(x = height, y = weight, colour = gender)
) + geom_point(size = 0.5, alpha = 0.5) + 
  stat_smooth(method = 'lm', se = F, fullrange = T) +
  theme_classic()
```

## Look at the data 

```{r show_data}
weight_df
```

## Variables names

This data has variables:

* gender
* weight
* height
* etc

1. gender
1. weight
1. height
1. etc

## We love math(s)

$$
y_i = \alpha + \beta x + \gamma_k^2 + \psi^2 + \Omega_k
$$